### 2023-04-01 main/chapter_experiment.tex
add pileup plot

Without high-energy hadron collisions in its centre, \atlas\ would be neutered.
For all of our data, we are therefore indebted to the LHC for so reliably
providing these exciting particle interactions.
We therefore begin this chapter with a description of the LHC itself in
Section~\ref{sec:atlas_lhc} before detailing the design of \atlas\ in
Section~\ref{sec:atlas_design}.

@@

% the LHC
% where the protons come from
Figure~\ref{fig:atlas_cern_complex}

\begin{figure}[tp]
\centering
\includegraphics[width=0.98\textwidth]{figures/atlas_lhc_complex.png}
\caption[
The CERN accelerator and detector complex, with the LHC as its largest piece
]{%
The CERN accelerator and detector complex, with the LHC as its largest piece
shown in dark blue-grey.
The complex uses a sequence of increasingly large and powerful accelerators to
boost ionised particles to their final collision energies in the LHC and to
yield beams for other CERN experiments.
This poster is adapted from~\cite{Haffner:1621894}.
}
\label{fig:atlas_cern_complex}
\end{figure}

% the accelerator complex
% RF cavities
% magnets (dipole, quadrupole etc)
% size of beam
% luminosity and its uncertainty
% pile-up

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A central slice of \atlas's design
]{%
A central slice of \atlas's design, reproduced from~\cite{atlas1999design1,
persint2014manual},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.6\textwidth]{figures/atlas_magnets.pdf}
\caption[
Layout of \atlas's toroidal magnets around the tile calorimeter and inner
solenoid
]{%
Layout of \atlas's toroidal magnets around the tile calorimeter and inner
solenoid, including the eight barrel and end-cap coils,
reproduced from~\cite{atlas2008experiment}.
The \atlas\ muon spectrometer measures muons' tracks as they bend through
this peripheral magnetic field.
}
\label{fig:atlas_magnets}
\end{figure}

>>>>

Without high-energy hadron collisions in its centre, \atlas\ would be neutered.
We are therefore indebted to the LHC for so reliably providing the exciting
hadron collisions that are necessary for all of our proton collision data.
We therefore begin this chapter with a description of the LHC itself in
Section~\ref{sec:atlas_lhc}, before detailing the design of \atlas\ in
Section~\ref{sec:atlas_design}.

@@

% the LHC
% where the protons come from
Figure~\ref{fig:experiment_cern_complex}

\begin{figure}[tp]
\centering
\includegraphics[width=0.99\textwidth]{figures/atlas_lhc_complex.png}
\caption[
The CERN accelerator and detector complex, with the LHC as its largest piece
]{%
The CERN accelerator and detector complex, with the LHC as its largest piece
shown in dark blue-grey.
The complex uses a sequence of increasingly large and powerful accelerators to
boost ionised particles to their final collision energies in the LHC and to
yield beams for other CERN experiments.
This poster is adapted from~\cite{Haffner:1621894}.
}
\label{fig:experiment_cern_complex}
\end{figure}

% the accelerator complex
% RF cavities
% magnets (dipole, quadrupole etc)
% size of beam
% luminosity and its uncertainty
% pile-up
\TODO{Distribution in the mean number of primary vertices per crossing, where the
variability in that mean arises from differing beam conditions over run-time.}
Figure~\ref{fig:experiment_run_2_mu}

\begin{figure}[tp]
\centering
\includegraphics[width=0.62\textwidth]{figures/atlas_pileup_mu_2015_2018.pdf}
\caption[
Mean number interactions per bunch crossing in Run~2 of the LHC
]{%
Mean number interactions per bunch crossing in Run~2 of the LHC;
rates presented are weighted by luminosity and sub-divided by year of
operation.
This figure includes all data that \atlas\ recorded with stable LHC proton
beams.
The reported integrated luminosities therefore exceed those we present later
in Table~\ref{tab:experiment_run2_state}, which are further filtered to require
other data-goodness criteria.
This figure is reproduced from~\cite{atlas_public_luminosity}.
}
\label{fig:experiment_run_2_mu}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.62\textwidth]{figures/atlas_cutaway_volume_1.pdf}
\caption[
A central slice of \atlas's design
]{%
A central slice of \atlas's design, reproduced from~\cite{atlas1999design1,
persint2014manual},
including a simulated event that interacts with several sensitive subsystems.
}
\label{fig:atlas_cutaway}
\end{figure}

@@

\begin{figure}[tp]
\centering
\includegraphics[width=0.62\textwidth]{figures/atlas_magnets.pdf}
\caption[
Layout of \atlas's toroidal magnets around the tile calorimeter and inner
solenoid
]{%
Layout of \atlas's toroidal magnets around the tile calorimeter and inner
solenoid, including the eight barrel and end-cap coils,
reproduced from~\cite{atlas2008experiment}.
The \atlas\ muon spectrometer measures muons' tracks as they bend through
this peripheral magnetic field.
}
\label{fig:atlas_magnets}
\end{figure}
